Accuracy, Stability, and Efficiency of Lattice Boltzmann Models in Simulating Non-Newtonian Fluid Flows

### 2015-12-23 main.tex
moving examples to non-Newtonian fluids breakdown enumeration

There are a number of complex fluids present in scientific problems and engineering applications that can be classified as non-Newtonian.
To name a few, pastes, slurries, molten plastics, polymer solutions, dyes, varnishes, suspensions, and some biomedical liquids like blood all behave in a non-Newtonian manner \cite{bohme1987non}.
Of all of the different non-Newtonian behaviors that exist, there are two major categories under which many of the behaviors fall:
\begin{enumerate}
	\item \emph{Yield stress fluids}. {\color{red} synopsis of yield stress fluids here}
	\item \emph{Power-law fluids}. {\color{red} synopsis of power-law fluids here}
	\item \emph{Other}. Many fluids either behave in a combination of the two ways described above or in another manner entirely.
\end{enumerate}

@@

Cement slurries and concretes are best modeled as non-Newtonian fluids because they exhibit a non-linear relationship between strain rate and shear stress.
In particular, cement slurries and concretes can be categorized as yield stress fluids. 
Yield stress fluids do not flow until a threshold value of stress, referred to as its yield stress, is exceeded.
Understanding the flow of cement slurries and concretes is important because they are used in the cementing of oil and gas wellbores, in construction, and blah blah blah.
If the cement job for an oil and gas wellbore is not completed successfully then gases and fluids can leak through the wellbore to contaminate ground water or the atmosphere ~\cite{grasinger2015simulation}.
The goal of understanding cement slurry and concrete flows during construction is to understand how construction forms can be completely filled as voids can lead to structural deficiencies ~\cite{RARR}.
Yield stress flow is relevant in many other disciplines and applications because of the many substances that can be modeled as Bingham plastics, e.g. pastes, paints, muds, molten plastics and metals, and blood \cite{wang2011lattice}. %MG: citation is for blood as non-Newtonian
Non-Newtonian flow is therefor relevant in the engineering and development of pastes and paints, flow and deformation of mud and clay in geotechnical engineering, understanding blood circulation in biomedical applications, materials science and manufacturing of metal and plastic parts, and in particular, the molding and casting of molten metals and plastics.

>>>>

There are a number of complex fluids present in scientific problems and engineering applications that can be classified as non-Newtonian.
To name a few, pastes, slurries, molten plastics, polymer solutions, dyes, varnishes, suspensions, and some biomedical liquids like blood all behave in a non-Newtonian manner \cite{bohme1987non}.
Of all of the different non-Newtonian behaviors that exist, there are two major categories under which many of the behaviors fall:
\begin{enumerate}
	\item \emph{Yield stress fluids}. Yield stress fluids do not flow until a threshold value of stress, referred to as its yield stress, is exceeded.
	\item \emph{Power-law fluids}. Power-law behavior is more commonly known as \emph{shear-thinning}--when the apparent viscosity decreases with increasing strain-rate--or \emph{shear-thickening}--when the apparent viscosity increases with increasing strain-rate. Shear-thinning fluids are also known as \emph{pseudoplastics}, some examples include polymer mixes and molten plastics.
	Shear-thickening fluids are also known as \emph{dilatants}, some examples include quicksand, a cornstarch and water mixture, and a silica and polyethylene glycol mixture.
	\item \emph{Other}. Many fluids have behavior that can be idealized as a combination of the two ways described above. Other fluids behave in another manner entirely.
\end{enumerate}

@@

Examples paragraph.

Cement slurries and concretes are best modeled as non-Newtonian fluids because they exhibit a non-linear relationship between strain rate and shear stress.
In particular, cement slurries and concretes can be categorized as yield stress fluids.

Understanding the flow of cement slurries and concretes is important because they are used in the cementing of oil and gas wellbores, in construction, and blah blah blah.
If the cement job for an oil and gas wellbore is not completed successfully then gases and fluids can leak through the wellbore to contaminate ground water or the atmosphere ~\cite{grasinger2015simulation}.
The goal of understanding cement slurry and concrete flows during construction is to understand how construction forms can be completely filled as voids can lead to structural deficiencies ~\cite{RARR}.
Yield stress flow is relevant in many other disciplines and applications because of the many substances that can be modeled as Bingham plastics, e.g. pastes, paints, muds, molten plastics and metals, and blood \cite{wang2011lattice}. %MG: citation is for blood as non-Newtonian
Non-Newtonian flow is therefor relevant in the engineering and development of pastes and paints, flow and deformation of mud and clay in geotechnical engineering, understanding blood circulation in biomedical applications, materials science and manufacturing of metal and plastic parts, and in particular, the molding and casting of molten metals and plastics.
